Choose a License

### 2024-11-28 choose_license.qmd
Mention the other case as well

If you are an employee at LMU and your funder does not mandate the use of a particular license, the decision which license to use lies with your associated chair. In the (rare) case the software you developed has a technical application and constitutes an invention, you are required to officially report your invention to the university which decides on its release. If the university claims the invention, you may not apply a copyright license that makes a patent grant. More information about this process is provided in the [service portal](https://www.serviceportal.verwaltung.uni-muenchen.de/internationals/research_transfer/intellectual_property/index.html). More information about software patents are provided by the FSFE: [Software Patents in Europe](https://fsfe.org/activities/swpat/swpat.en.html).
:::

>>>>

If you are an employee at LMU and your funder does not mandate the use of a particular license, the decision which license to use lies with your associated chair. In the (rare) case the software you developed has a technical application and it falls under the legal definition of an invention, you are required to officially report your invention to the university which decides on its release. If the university claims the invention, you may not apply a copyright license that makes a patent grant. In all other cases you are free to license your research project as you like.

More information about th invention disclosure process can be found in the [service portal](https://www.serviceportal.verwaltung.uni-muenchen.de/internationals/research_transfer/intellectual_property/index.html). More information about software patents are provided by the FSFE: [Software Patents in Europe](https://fsfe.org/activities/swpat/swpat.en.html).
:::
